### 2021-04-03 Chapter-3/Chapter-3.tex
update

  \begin{tabular}{lrrrrrr}

@@

                                               &                        &                     &                      &              & ms                     \\\cline{6-6}
      AES &             & 68                     & 0                   & 68                   & 39,855        & 512     \\
      AES &                & 68                     & 0                   & 68                   & 39,855       & 520         \\
      AES &                & 75                     & 0                   & 75                   & 1,704        & 231       \\
      AES &                & 88                     & 0                   & 88                   & 1,350        & 36     \\
      AES&           & 88                     & 0                   & 88                   & 1,350        & 35   \\
      AES &         & 88                     & 0                   & 88                   & 1,420        & 36    \\
      AES &        & 88                     & 0                   & 88                   & 1,586        & 43      \\

@@

                         &    &                    &                     &                      &                  & seconds                  \\\cline{6-6}

@@

                         &                        &                     &                      &                 & minutes            \\\cline{6-6}
      RSA &           & 6                       & 6                   & 0                    & 22,109,246    & 39      \\
      RSA &            & 12                      & 12                  & 0                    & 24,484,441    & 44        \\
      RSA &           & 107                    & 105                 & 2                    & 17,002,523   & 23  \\
      RSA &           & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
      RSA &           & 36                     & 27                  & 9                    & 15,285,210   & 40      \\
      RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
      RSA &         & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
      RSA &            & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
      RSA & & 11& 9& 2& 9,527,231& 2 \\
      RSA & & 14& 14& 0& 10,513,606& 14  \\
      RSA &        & 8                      &  8                  & 0                    & 27,407,986    & 113    \\

>>>>

  \begin{tabular}{llrrrrr}

@@

                                               &                        &                     &                      &              & ms                     \\\cline{7-7}
      AES &  mbedTLS 2.5   & 68                     & 0                   & 68                   & 39,855        & 512     \\
      AES &  mbedTLS 2.15   & 68                     & 0                   & 68                   & 39,855       & 520         \\
      AES &  OpenSSL 0.9.7        & 75                     & 0                   & 75                   & 1,704        & 231       \\
      AES &  OpenSSL 1.0.2f       & 88                     & 0                   & 88                   & 1,350        & 36     \\
      AES&   OpenSSL 1.0.2k       & 88                     & 0                   & 88                   & 1,350        & 35   \\
      AES &  OpenSSL 1.1.0f     & 88                     & 0                   & 88                   & 1,420        & 36    \\
      AES & OpenSSL 1.1.1      & 88                     & 0                   & 88                   & 1,586        & 43      \\

@@

                         &    &                    &                     &                      &                  & seconds                  \\\cline{7-7}

@@

                         &                        &                     &                      &                 & minutes            \\\cline{7-7}
      RSA &           & 6                       & 6                   & 0                    & 22,109,246    & 39      \\
      RSA &            & 12                      & 12                  & 0                    & 24,484,441    & 44        \\
      RSA &           & 107                    & 105                 & 2                    & 17,002,523   & 23  \\
      RSA &           & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
      RSA &           & 36                     & 27                  & 9                    & 15,285,210   & 40      \\
      RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
      RSA &         & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
      RSA &            & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
      RSA & & 11& 9& 2& 9,527,231& 2 \\
      RSA & & 14& 14& 0& 10,513,606& 14  \\
      RSA &        & 8                      &  8                  & 0                    & 27,407,986    & 113    \\
